\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{titling}
\usepackage{geometry}
\usepackage{hyperref}

\hypersetup{
	colorlinks=false
	linktoc=all
	linkcolor=black
}
\graphicspath{{./images/}}

\title{Project 3 Outline \\
	\large Team 228}
\author{Chad Lape, Demitri Laikos, Jacob Brown, and Noah Heinen}
\date{February 16, 2020}



\setlength{\droptitle}{-4em}

\begin{document}
	\maketitle
	
	\tableofcontents
	
	\newpage
	\section{Grand Challenge}
	
	Team 228 will complete project 4 on the Engineering Grand challenge regarding the personalization of education. This being a major problem which may affect for years to come as each school is not equal in its ability to provide a proper education to the youth.
	
	\newpage
	\section{Data Sources}
	There are a number of data sources our team believes we will use. These sources of information are important to the project as they will govern what information our group will gather. 
	
	\subsection{Data.gov}
	This is a government data source which we believe may contain a wealth of information on education within the United States. This being information pertaining to standardized testing and other information.
	
	\subsection{data.un.org}
	This will give international information and can help make the case for a larger group of people in many other countries and livelihoods. This should be key to finding more information on variables like education doctrine and as such is needed. This is trustworthy due to the data coming from the UN which is a coalition of countries and should be accurate by its need.
	
	\subsection{UC Libraries}
	This collection of information comes from the university and subsidies found within this is likely to be accurate and can be used as a third party to information gathered from other sources. Otherwise, it can also be used as a base for sources of information locally and internationally due to UC having sources from all over the globe. UC is also one of the research universities within a network of them and should have more information that can be used.
	
	\newpage
	\section{Variables}
	This is the definition of possible variables which may define the problem and how it will change over time.
	
	\subsection{Income}
	It seems likely that income will be a variable in how education is handled throughout the world. This is due to areas with larger amounts of money being able to pay teachers more and likely hire more than enough teachers and have up to date resources ready within the school. This is likely to be a large factor as well as in a preliminary analysis it would seem that areas of higher income tend to have less crime and this might have some effect on the quality of schools in the area.
	
	\subsection{Government}
	How the government of the area handles education may also have an affect on the quality of education received. Having more universal policies and an education which is able to adapt to the person who is receiving it is important to keeping a well educated region. If a government is prone to mishandle money or not provide funds to schools which needs them, it would also tend to have an effect on this.
	
	\subsection{Technology}
	Likely, regions which have a larger integration with modern technology are going to be more able to adopt different technological answers to the problem of education. This may provide some trouble in regions if they are unable to access the resources which are then able to be used to provide a personalized education. 
	
	\newpage
	\section{Project Management}
\end{document}
